# US Military Deployments and Minority Communities {#minority-chapter}

This chapter provides supplementary information related to Chapter 4 of the book, focusing on how US military deployments interact with and are viewed by minority communities. 


```{r setup, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(tidyr)
library(data.table)
library(job)
library(broom)
library(broom.mixed)
library(modelr)
library(cshapes)
library(countrycode)
library(dagitty)
library(ggdag)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(arm)
library(brms)
library(rstan)
library(cmdstanr)
library(parallel)
library(tidybayes)
library(scales)
library(ggdist)
library(ggh4x)
#library(ggtrack)
library(viridis)
library(kableExtra)
library(BayesPostEst)
library(texreg)
library(modelsummary)
library(gt)
library(webshot)
library(kableExtra)
library(ggExtra)
library(ggrepel)
library(ggmcmc)
library(ggpubr)
library(ggtext)
library(patchwork)
library(here)
library(performance)
library(tictoc)
library(sysfonts)
library(remotes)
library(formattable)
library(sparkline)
library(ltxsparklines)


knitr::opts_chunk$set(comment = '', dpi = 400, warning = FALSE, echo = FALSE, message = FALSE)

sysfonts::font_add_google("Oswald", family = "oswald")
showtext::showtext_auto()

# Set basesize for fonts in plots
basesize <- 11


# Regular plot theme
theme_flynn <- function(){ 
  
      theme_linedraw(base_size = basesize, base_family = "oswald") %+replace% 
        
        theme(plot.title = element_text(face = "bold", size = basesize * 1.3, hjust = 0, margin = margin(t = 0, b = 0.3, l = 0, r = 0, unit = "cm")),
              plot.subtitle = element_text(size = basesize),
              plot.caption = element_text(face = "italic", size = basesize * 0.6),
              panel.border = element_rect(fill = NA, size = 0.2),
              strip.background = element_rect(fill = "gray80", color = "black", size = 0.2),
              strip.text = element_text(size = basesize, color = "black", face = "bold", margin = margin(t = 0.2, b = 0.2, l = 0.2, r = 0.2, unit = "cm")),
              panel.background = element_rect(size = 0.2),
              panel.grid.major = element_line(color = "gray70", size = 0.15),
              panel.grid.minor = element_line(color = "gray90", size = 0.1),
              axis.title = element_text(face = "bold", size = basesize),
              axis.title.y = element_text(angle = 90, margin = margin(t = 0, r = 0.5, b = 0, l = 0, unit = "cm")),
              axis.title.x = element_text(margin = margin(t = 0.5, r = 0, b = 0, l = 0, unit = "cm")),
              axis.ticks = element_line(size = 0.1),
              axis.ticks.length = unit(0.1, "cm"),
              legend.title = element_text(size = basesize, face = "bold", hjust = 0, margin = margin(t = 0, b = 0, l = 0, r = 0, unit = "cm")),
              plot.margin = margin(0.5, 0.5, 0.5, 0.5, unit = "cm"),
              legend.margin = margin(t=-10, b=0, r=0, l=0),
              legend.box.margin = margin(-10,-10,-10,-10))
  }

# Map version of theme
theme_flynn_map <- function(){
  
  theme_void(base_family = "oswald") %+replace% 
    
    theme(plot.title = element_text(face = "bold", size = 18, hjust = 0, margin = margin(t = 0, b = 0.3, l = 0, r = 0, unit = "cm")),
          plot.subtitle = element_text(size = 12, hjust = 0, margin = margin(t = 0, b = 0.3, l = 0, r = 0, unit = "cm")),
          plot.caption = element_text(face = "italic", size = 8, hjust = 1, margin = margin(t = 0.2, unit = "cm")),
          strip.background = element_rect(fill = "gray80", color = "black"),
          strip.text = element_text(color = "black", face = "bold"),
          panel.grid.major = element_line(color = "white", size = 0),
          panel.grid.minor = element_line(color = "white", size = 0),
          #axis.title = element_text(face = "bold", size = 0),
          #axis.title.y = element_text(margin = margin(t = 0, r = 0.5, b = 0, l = 0, unit = "cm")),
          #axis.title.x = element_text(margin = margin(t = 0.5, r = 0, b = 0, l = 0, unit = "cm")),
          legend.title = element_text(face = "bold"),
          legend.position = "bottom",
          legend.key.height = unit(0.6, "cm"),
          legend.key.width = unit(2.5, "cm"))
}


ccode.list <- c("200", "210", "211", "230", "235", "255", "290", "325", "640", "690", "732", "740", "840", "900")


### Stan Setup ####

# Conflicted pckage really fucks things up
if(any(grepl("package:conflicted", search()))) detach("package:conflicted") else message("package conflicted not loaded")


# Parallelize machine
options(mc.cores = parallel::detectCores())
ncores <- parallel::detectCores()
rstan_options(auto_write = TRUE)


# Load opinion data for individual-level protest models.
load(here::here("../Book/Data/General", "opinion.data.RData")) 

# This fixes an encoding issue which duplicated the "Other" category unnecessarily. 
o.data <- setDT(o.data)[
  , relig := ifelse(grepl("Other", relig), "Other", relig)
]

set.seed(seed = 66502)


# Load model files because bookdown doesn't like something about reading the brms rds files in.

# Bivariate models for illustrative purposes
m.t1 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.t1.rds"))
m.g1 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.g1.rds"))
m.p1 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.p1.rds"))

# Full models
m.t2 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.t2.rds"))
m.g2 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.g2.rds"))
m.p2 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.p2.rds"))

# Models focusing on Japan
m.t2.japan <- readRDS(here::here("../Book/Output/Chapter-Minority/m.t2.japan.rds"))
m.g2.japan <- readRDS(here::here("../Book/Output/Chapter-Minority/m.g2.japan.rds"))
m.p2.japan <- readRDS(here::here("../Book/Output/Chapter-Minority/m.p2.japan.rds"))

m.t3 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.t3.rds"))
m.g3 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.g3.rds"))
m.p3 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.p3.rds"))

m.t4 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.t4.rds"))
m.g4 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.g4.rds"))
m.p4 <- readRDS(here::here("../Book/Output/Chapter-Minority/m.p4.rds"))

m.t4.japan <- readRDS(here::here("../Book/Output/Chapter-Minority/m.t4.japan.rds"))
m.g4.japan <- readRDS(here::here("../Book/Output/Chapter-Minority/m.g4.japan.rds"))
m.p4.japan <- readRDS(here::here("../Book/Output/Chapter-Minority/m.p4.japan.rds"))

priors.t <- brms::prior_summary(m.t1) 
priors.g <- brms::prior_summary(m.g1)
priors.p <- brms::prior_summary(m.p1)

priors.t2 <- brms::prior_summary(m.t2) 
priors.g2 <- brms::prior_summary(m.g2)
priors.p2 <- brms::prior_summary(m.p2)

priors.t2.japan <- brms::prior_summary(m.t2.japan) 
priors.g2.japan <- brms::prior_summary(m.g2.japan)
priors.p2.japan <- brms::prior_summary(m.p2.japan)

```


## Descriptive Information

```{r minority-description, echo=FALSE, warning=FALSE, message=FALSE}

# Minorities as a percent of the sample by year
# # Note that I had to edit this code chunk and changed the `length(X1)` line relative tot he original code because the original code was spitting back "1" for the observation count for 2020 for all countries. No idea why.
minperc <- o.data %>% 
  group_by(country, year) %>% 
  mutate(minority.yes = ifelse(minority == "Yes", 1, 0),
         groupobs = length(X1)) %>% 
  dplyr::summarise(minority = sum(minority.yes, na.rm = TRUE),
            obs = mean(groupobs, na.rm = TRUE)) %>% 
  mutate(min.per = minority/obs) %>% 
  filter(!is.na(country))

ggplot(minperc, aes(y = factor(year), x = min.per, color = country)) +
  geom_text(aes(label = country), position = position_jitter(height = 0.4), size = 2.5) +
  theme_flynn() +
  scale_x_continuous(labels = scales::percent_format()) +
  guides(color = FALSE) +
  theme(plot.title.position = "plot") +
  labs(x = "Percent",
       y = "Year",
       color = "Country",
       title = "Self-identified minority group members as percent of country sample")

```

### Further Discussion from Chapter 5

Comparing the minority variable coefficients with coefficients for the other variables is informative. Also note that the coefficients for the Non-Binary gender identity category throws off the visual scale of the remaining coefficients. First, looking at the age variables, we can see that the older age cohort tends to have a higher likelihood of expressing a positive view of all three US groups than younger age cohorts. Older age cohorts also appear to be less likely to express a negative view of US actors than younger groups, except for views of the US government where we see older age groups more likely to express both positive and negative views.  The reference category here is the 18--24 age cohort, meaning that we should evaluate all of the coefficients concerning that baseline. However, we can still compare the coefficient values of the other groups but need to be cautious where there is a significant overlap between the posterior distributions. 

Individuals with more education appear to be more likely to express both positive and negative views of US actors. However, there is no clear indication that more education correlates with larger differences in negative versus positive views. As we discuss in Chapter 2, this likely reflects a similar process whereby individuals with more education simply have more informed opinions, one way or the other.

Regarding gender, individuals identifying as female tend to be less likely to express positive views than those who identify as male. Those individuals identifying as non-binary also appear less likely to express positive views of US actors, and are more likely to express negative views of US troops and the US government, with some indication of a lower probability of expressing negative views of the American people.

Finally, when comparing across income quintiles, we find some interesting patterns. First, the baseline category here is the lowest income grouping---the 0--20\% quintile. Compared to this group, there is some indication that higher income groups tend to have slightly less favorable views of US military personnel, but these differences appear very small. We find a similar pattern when looking at views of the US government, where only the highest income group shows a slightly positive coefficient value. When looking at views of the US people, groups above the 40\% income group appear to have a slightly more positive probability of expressing positive views than the bottom two income categories. We find somewhat similar patterns when looking at negative views. However, we do see larger differences in the probability of expressing negative views among the highest income groups when looking at views of the US government. Though not depicted in this figure, a notable feature of these results is that income appears to correlate quite strongly with a lower probability of respondents saying "Don't Know/Decline to Answer" when asked about any of the three US groups. Only 2.7\% of the highest income groups across all 14 countries replied "Don't Know/Decline to Answer" when asked about the US military presence in their country. On the other hand, 7.7\% of respondents in the lowest income group gave the same response. Like education, income appears to correlate more strongly with more informed opinions instead of clearly lining up with more positive or more negative attitudes. 



### Prior Specification Tables for Minority Models

```{r prior-info-crime-troops, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.t, caption = "Priors specifications for bivariate Troops contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-gov, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.g, caption = "Priors specifications for bivariate Government contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-people, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.p, caption = "Priors specifications for bivariate People contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-troops-2, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.t2, caption = "Priors specifications for full Troops contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-gov-2, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.g2, caption = "Priors specifications for full Government contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-people-2, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.p2, caption = "Priors specifications for full People contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-troops-japan, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.t2.japan, caption = "Priors specifications for full Japan Troops contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-gov-japan, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.g2.japan, caption = "Priors specifications for full Japan Government contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```

```{r prior-info-crime-people-japan, warning=FALSE, echo=FALSE, message=FALSE}

kableExtra::kable(priors.p2.japan, caption = "Priors specifications for full Japan People contact models.", digits = 3) |> 
  kableExtra::kable_styling(font_size = 11) |> 
  kableExtra::scroll_box(height = "400px", width = "100%")

```




### Posterior Predictive Check Figures

```{r posterior-check-crime-troops, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for bivariate contact models and attitudes towards the US troops outcome variable."}
check.t <- brms::pp_check(m.t1, ndraws = 100, type = "bars_grouped", group = "country") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for Troops Model")

check.t

```

```{r posterior-check-crime-gov, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for bivariate contact models and attitudes towards the US government outcome variable."}
check.g <- brms::pp_check(m.g1, ndraws = 100, type = "bars_grouped", group = "country") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for Government Model")

check.g

```


```{r posterior-check-crime-people, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for bivaraite contact models and attitudes towards the US people outcome variable."}
check.p <- brms::pp_check(m.p1, ndraws = 100, type = "bars_grouped", group = "country") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for People Model")

check.p

```




```{r posterior-check-crime-troops-2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for full contact models and attitudes towards the US troops outcome variable."}
check.t2 <- brms::pp_check(m.t2, ndraws = 100, type = "bars_grouped", group = "country") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for Troops Model")

check.t2

```

```{r posterior-check-crime-gov-2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for full contact models and attitudes towards the US government outcome variable."}
check.g2 <- brms::pp_check(m.g2, ndraws = 100, type = "bars_grouped", group = "country") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for Government Model")

check.g2

```


```{r posterior-check-crime-people-2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for full contact models and attitudes towards the US people outcome variable."}
check.p2 <- brms::pp_check(m.p2, ndraws = 100, type = "bars_grouped", group = "country") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for People Model")

check.p2

```






```{r posterior-check-crime-troops-2-japan, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for contact models and attitudes towards the US troops outcome variable. Models look at Japan only and contain varying effects for minority status across provinces."}
check.t2.japan <- brms::pp_check(m.t2.japan, ndraws = 100, type = "bars_grouped", group = "province") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for Troops Model")

check.t2.japan

```

```{r posterior-check-crime-gov-2-japan, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for contact models and attitudes towards the US government outcome variable. Models look at Japan only and contain varying effects for minority status across provinces."}
check.g2.japan <- brms::pp_check(m.g2.japan, ndraws = 100, type = "bars_grouped", group = "province") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for Government Model")

check.g2.japan

```


```{r posterior-check-crime-people-2-japan, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior predictive checks for contact models and attitudes towards the US people outcome variable. Models look at Japan only and contain varying effects for minority status across provinces."}
check.p2.japan <- brms::pp_check(m.p2.japan, ndraws = 100, type = "bars_grouped", group = "province") +
  theme_flynn() +
  labs(title = "Posterior Predictive Check for People Model")

check.p2.japan

```


